\tname: A Database of Reproducible Bugs in Deep Learning Libraries to Enable Systematic Evaluation of Testing Techniques

### 2025-01-14 paper/main.tex
added some comments

\textbf{Example}~\Fix{Can you show here the artifacts associated to bug
  120903 that you will use in the next section? If it takes too much
  space, show only directory with files and the test case.}

@@

The second step runs the \tname's command \CodeIn{run-tool}, which
proceeds in two steps (1) reproduce the bug separately, as done with
command \CodeIn{run-test}, and (2) then update the environment inside
the docker container of the tool to run the tool with the script
provided.\Fix{is the container destroyed after that? you are changing
  the environment for a certain bug, right?!} The first step is a
sanity check to assure that the bug can indeed be reproduced. For
example, the following command runs FreeFuzz on the enviroment of the
bug associated with the issue 117033 from \torch.

>>>>

\textbf{Example}~\Fix{Can you show here the artifacts associated to bug
  120903 that you will use in the next section? If it takes too much
  space, show only directory with files and the test case. - Abid: by the test case, do you mean the python code used to reproduce the bug?}

@@

The second step runs the \tname's command \CodeIn{run-tool}, which
proceeds in two steps (1) reproduce the bug separately, as done with
command \CodeIn{run-test}, and (2) then update the environment inside
the docker container of the tool to run the tool with the script
provided.\Fix{is the container destroyed after that? you are changing
  the environment for a certain bug, right?! - Abid: the dependencies are installed inside the docker, but after running the dependencies are not reverted back. if another bug is to be reproduced, installing the new dependencies will simply overwrite the previous dependencies} The first step is a
sanity check to assure that the bug can indeed be reproduced. For
example, the following command runs FreeFuzz on the enviroment of the
bug associated with the issue 117033 from \torch.
